Simulated Contaminant Summary
========================================================
## Dataset description:

## Methods summary:

## Results

```{r echo=FALSE, message=FALSE}
#loading required packages and sourcing files
library(ggplot2)
library(stringr)
library(reshape2)
library(plyr)
source("file_locations.R")
sim_matches <- read.csv(str_c(path_results_directory,"/sim_contam_matches.csv", sep=""), stringsAsFactor = F)
for(i in c("org1_tid","org2_tid","size")){
  sim_matches[,i] <- as.factor(sim_matches[,i])
}
```

### Experimental design
Number of organisms: `r length(unique(sim_matches$org1))`       
Organisms: `r unique(sim_matches$org1_tid)`   
Pairwise mixtures of each organism combinations    
Number of Proportions: `r length(unique(sim_matches$prop1))`     
Contaminant Proportions: `r unique(sim_matches$prop2)`   
**Total datasets:** `r length(unique(sim_matches$input_filename))`   


### Summary of matches
```{r}
sim_unique_counts <- ddply(sim_matches, .(org1_tid, size), summarize, count = length(unique(match_tid)))
ggplot(sim_unique_counts) + 
  geom_boxplot(aes(x = size, y = count), color = "grey") +
  geom_point(aes(x = size, y = count, color = org1_tid), size = 4) + 
  geom_line(aes(x = as.numeric(size), y = count, color = org1_tid)) +
  labs(x = "Read Size (bp)", y = "Number of hits to unique organisms", color = "Organism")+
  theme_bw()
```
#### Observations: 
Between 50 and 200 unique organism hits for each of the dataset combinations.  The difference in the number of unique matches has a much larger decrease compared to single organisms.  
Questions:  
1. can ask similar questions to single organisms   
2. how do the unique matches compare for single and contaminanted datasets.    
Note- that the contaminated dataset counts are based on the unqiue matches for 64 datasets, 6 contaminants and 9 mixtures.  


#### LOD by organism and contaminant
```{r}
sim_LOD <- ddply(.data=sim_matches[grep("org2",sim_matches$match),],
                 .variables=.(size, org1_tid, org2_tid, org2_match), 
                 summarize, LOD = min(prop2))
sim_LOD$org2_match <- factor(sim_LOD$org2_match, levels = c("exact", "species", "genus","family","order","class", "phylum"))
```
Limit of detection is defined as the proportion of contaminant with the lowest proportion.  The contaminant proportion is representative of the proprotion of the sample and not the proportion of reads.
```{r fig.width=12}
ggplot(sim_LOD) + 
  geom_bar(aes(x = org1_tid, y = LOD, fill = size), stat = "identity", position = position_dodge(width = 1.5), width = 0.75) + 
  geom_hline(aes(yintercept = c(0.01, 0.0001, 0.0000025)), linetype = 2) + 
  facet_grid(~org2_tid, scale = "free_x") + scale_y_log10() +   
  theme_bw() +
  theme(axis.text.x=element_text(angle=-90)) +
  labs(x = "Target Organism", fill = "Read Size (bp)", y = "Limit of Detection")
```
Matches at any level to the contaminant genome.

```{r message=FALSE, fig.height=6, fig.width=18}
ggplot(sim_LOD) + 
  geom_point(aes(x = org1_tid, y= LOD, color = org2_match),alpha = 0.75, position = position_dodge(width = 0.5), size = 3) +
  geom_line(aes(x = org1_tid, y = LOD)) +
  labs(linetype = "Read Size (bp)", x = "Match Level") + 
  scale_y_log10() + 
  theme_bw() +
  theme(axis.text.x=element_text(angle=-90)) +
  facet_grid(size~org2_tid, scale = "free")
```
```{r}
LOD_table <-dcast(sim_LOD,org2_tid*org1_tid~org2_match*size, value.var = "LOD", fill= "")
```
```{r results='asis', echo=FALSE}
 library(xtable)
  print(xtable(LOD_table),type='html')
```

Observations: For a number of combinations the limit of detection is lower for 75 bp compared to 250 bp simulated datasets.  Need to look into the data to make sure this is not due to a bug in the code.

### Quantitaive analysis
Comparison of final guess values with proportions for exact matches only
```{r fig.width=12, fig.height=12}
sim_exact <- ddply(sim_matches[sim_matches$org2_match == "exact",], .(org1_tid,org2_tid,prop1, prop2, size), summarize, est_prop = sum(Final.Guess))
ggplot(sim_exact) + 
  geom_abline(aes(yintercept = 0, slope = 1), linetype = 2) +
  geom_line(aes(x = prop2, y = est_prop, color = as.character(size))) + 
  facet_grid(org1_tid~org2_tid) +
  theme_bw() + 
  theme(axis.text.x=element_text(angle=-90))
ggplot(sim_exact) + 
  geom_abline(aes(yintercept = 0, slope = 1), linetype = 2) +
  geom_line(aes(x = prop2, y = est_prop, color = as.character(size))) + 
  facet_grid(org1_tid~org2_tid) +
  theme_bw() + 
  coord_cartesian(ylim = c(0,0.05)) +
  theme(axis.text.x=element_text(angle=-90))
```
```{r fig.width = 12}
sim_exact$diff <- sim_exact$prop2 - sim_exact$est_prop
ggplot(sim_exact) + geom_boxplot(aes(x = org2_tid, y = diff, fill = org1_tid), alpha = 0.75) + facet_wrap(~size) + theme_bw()
```

#Need to figure out a better way to present these resutls
