Summary of EC single organsism simulated datasets
========================================================
```{r echo=FALSE, message=FALSE}
#loading required packages and sourcing files
library(ggplot2)
library(stringr)
library(reshape2)
library(plyr)
library(xtable)
source("file_locations.R")
source("match_tid.R")
sim_matches <- read.csv(str_c(path_results_directory,"/sim_EC_matches.csv", sep=""), stringsAsFactor = F)
```
# Dataset description:
Paired end Illumina reads simulated using ART read simulator for the following organisms (Table 1).
```{r echo =FALSE}
org_tid <- unique(sim_matches$org_tid)
org_name <- c()
for(i in org_tid){
  org_name <- c(org_name,python.call("getNameByTaxid", i))
}
org_df <- data.frame(tid = org_tid, name = org_name)
```
```{r results='asis'}
print(xtable(org_df),type='html')
```


## Summary of matches
```{r}
sim_matches <- read.csv(str_c(path_results_directory,"/sim_EC_matches.csv", sep=""), stringsAsFactor = F)
```
Large number of organisms from multiple genus - will want to create table of taxonomic level to be able to facet graphs by different shared levels.
### Number of unique Match org hits per combination
```{r}
sim_unique_counts <- ddply(sim_matches, .(org_tid, size), summarize, count = length(unique(match_tid)))
sim_unique_counts$size <- as.factor(sim_unique_counts$size)
ggplot(sim_unique_counts) + 
  geom_boxplot(aes(x = size, y = count), color = "grey") +
  geom_point(aes(x = size, y = count, color = as.character(org_tid)), size = 4) + 
  geom_line(aes(x = as.numeric(size), y = count, color = as.character(org_tid))) +
  labs(x = "Read Size (bp)", y = "Number of hits to unique organisms", color = "Organism")+
  theme_bw()
```
#### Observations:

### Quantitaive analysis
Evlauation of match proportion distribtions
```{r }
sim_match_sum <- ddply(sim_matches, .(org, size, match), summarize, prop = sum(Final.Guess))
sim_match_sum$match <- factor(sim_match_sum$match, levels = c("exact", "species", "genus","family","order","class", "phylum","no match"))
ggplot(sim_match_sum) + geom_jitter(aes(x = as.numeric(match), y = prop, color = as.character(size)), alpha = 0.5) +
  theme_bw() +
  theme(axis.text.x=element_text(angle=-90)) +
  scale_x_continuous(breaks = 1:length(levels(sim_match_sum$match)), labels = levels(sim_match_sum$match)) +
  labs(x = "Match Classification", y = "Match Proportion", linetype = "Read Size (bp)")
```

Do the results look better as a table or a graph?
```{r}
sim_match_sum$prop <- round(sim_match_sum$prop, 3)
sim_match_table <- dcast(sim_match_sum,
                         org*size~match,
                         value.var = "prop", fill = "")
```
```{r results='asis', echo=FALSE}
 library(xtable)
print(xtable(sim_match_table),type='html')
```
