Summary of single organism data analysis
========================================================
# Dataset description:

# Methods summary:

# Results

```{r echo=FALSE, message=FALSE}
#loading required packages and sourcing files
library(ggplot2)
library(stringr)
library(reshape2)
library(plyr)
library()
source("file_locations.R")
```

## Summary of matches
```{r}
sim_matches <- read.csv(str_c(path_results_directory,"/sim_single_matches.csv", sep=""), stringsAsFactor = F)
```

### Number of unique Match org hits per combination
```{r}
sim_unique_counts <- ddply(sim_matches, .(org_tid, size), summarize, count = length(unique(match_tid)))
sim_unique_counts$size <- as.factor(sim_unique_counts$size)
ggplot(sim_unique_counts) + 
  geom_boxplot(aes(x = size, y = count), color = "grey") +
  geom_point(aes(x = size, y = count, color = as.character(org_tid)), size = 4) + 
  geom_line(aes(x = as.numeric(size), y = count, color = as.character(org_tid))) +
  labs(x = "Read Size (bp)", y = "Number of hits to unique organisms", color = "Organism")+
  theme_bw()
```
#### Observations:
For all organisms the number of unqiue matches decreases with increase in the length of the simulated reads.     
Questions:   
1. How do the differences in number of unique matches compare?      
2. How does the ranks compare (who has the largest drop in matches with the increase in size)?   

### Quantitaive analysis
Evlauation of match proportion distribtions
```{r }
sim_match_sum <- ddply(sim_matches, .(org_tid, size, match), summarize, prop = sum(Final.Guess))
sim_match_sum$match <- factor(sim_match_sum$match, levels = c("exact", "species", "genus","family","order","class", "phylum","no match"))
ggplot(sim_match_sum) + geom_line(aes(x = as.numeric(match), y = prop, linetype = as.character(size))) +
  theme_bw() +
  theme(axis.text.x=element_text(angle=-90)) +
  scale_x_continuous(breaks = 1:length(levels(sim_match_sum$match)), labels = levels(sim_match_sum$match)) +
  labs(x = "Match Classification", y = "Match Proportion", linetype = "Read Size (bp)") + facet_wrap(~org_tid)
```

Do the results look better as a table or a graph?
```{r}
sim_match_sum$prop <- round(sim_match_sum$prop, 3)
sim_match_table <- dcast(sim_match_sum[sim_match_sum$prop > 0.000,],org_tid*size~match,value.var = "prop", fill = "")
```
```{r results='asis', echo=FALSE}
 library(xtable)
  print(xtable(sim_match_table),type='html')
```

## Conclusions   
As expected the quality of the matches increases significantly read size.  For 250 bp reads, contaminats are theoretically easily detected when the lowest common taxonomic level is genus or higher.